Towards Compiler-Agnostic Performance in Finite-Difference Codes. (TBC)

### 2014-11-12 shallow_perf.tex
Move to expecting IEEEtran.cls to already be installed. Include bargraph.pl with the source for this paper

% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{./IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The compilers and CPUs used in this work.}
\label{TABLE_compilers}
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
                 & Gnu   & Intel       & Cray    & IBM bgxlf\\
\hline
Intel Haswell    & 4.8.2 & 14.0.0      &         &          \\
Intel Ivy Bridge &       & 14.0.1.106  & 8.3.3   &          \\
IBM A2 (BGQ)     &       &             &         & 14.1     \\
IBM Power 8      &       &             &         &          \\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The compiler flags used in this work.}
\label{TABLE_compiler_flags}
\centering
\begin{tabular}{|l|c|}
\hline
Compiler  &  Flags \\
\hline
Gnu       & -Ofast -mtune=native -finline-limit=50000    \\
Intel     & -O3 -fast -fno-inline-factor    \\
Cray      & -O3 -O ipa5 -h wp    \\
IBM bgxlf & -O5 -qinline=auto:level=10    \\
\hline
\end{tabular}
\end{table}

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

>>>>

% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The matrix of compilers and CPUs used in this work. The use
  of a compiler on a given CPU is indicated by the specification of
  the version of the compiler in the relevent element. No entry
  indicates that a compiler was not available/used on that CPU.}
\label{TABLE_compilers}
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
                 & \multicolumn{4}{c|}{Compiler}             \\
\hline
                 & Gnu   & Intel       & Cray    & IBM bgxlf\\
\hline
Intel Haswell    & 4.8.2 & 14.0.0      &         &          \\
Intel Ivy Bridge &       & 14.0.1.106  & 8.3.3   &          \\
IBM A2 (BGQ)     &       &             &         & 14.1     \\
IBM Power 8      &       &             &         &          \\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The compiler flags used in this work.}
\label{TABLE_compiler_flags}
\centering
\begin{tabular}{l|c}
\hline
Compiler  &  Flags \\
\hline
Gnu       & -Ofast -mtune=native -finline-limit=50000    \\
Intel     & -O3 -fast -fno-inline-factor    \\
Cray      & -O3 -O ipa5 -h wp    \\
IBM bgxlf & -O5 -qinline=auto:level=10    \\
\hline
\end{tabular}
\end{table}

@@
